Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-05 Abstract.tex
Sketching out

This dissertation presents a method for modelling disclosure behaviour
by treating the interaction as paired signalling games played by decision
theoretic agents. Two theories of decision making - Bayesian risk
minimisation, and \ac{CPT} - are investigated, and a simulation developed
using Python.

The feasibility of the method is examined through a case study, which
considers the disclosure of the drinking behaviour of pregnant women
to their midwives.

The essence of the scenario is that there is considered to be a long
term benefit to disclosure - common in the healthcare arena, but an
opportunity cost associated with disclosure. In the case study, this
is conceptualised as arising from the perceived undesirability of
drinking while pregnant. More generally this could derive from any
imbalance in the long term benefit and the opportunity cost, for example
the subjective benefit of a cigarette in the near future, versus the
discounted benefit of better health later.

Theories of decision are driven by the weighing of probabilities and
subjective gains or losses. In this case, the probabilities are generated
by individual agents based on their initial preconceptions and their
experiences across the simulation, using Bayesian inference.

The Bayesian risk minimising model is able to reproduce qualitative
trends around increased honesty over appointments, and a negative
impact of harsh judgement of drinkers on disclosure. The \ac{CPT}
model is less successful, which may be a result of improper, or excessively
homogenous parameters, in combination with unrealistic payoffs.

A global sensitivity analysis is also conducted using Gaussian Emulation
Machines, and finally recommendations for further work are dervived, along
with a few key recommendations for practice - assume people are being honest,
and be non-judgemental.

\vfill{}

\endgroup

>>>>

\subsection*{Background}

We draw together methodologies from game theory, agent based modelling, and decision theory to explore the process of decision making around disclosure. This is framed in the context of pregnant women disclosing their drinking behaviour to their midwives.

\subsection*{Objective}

The primary purpose it to demonstrate the potential utility of an approach which it is hoped goes some way towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents. To this end we hope to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of producing trends from the literature.
We also seek to demonstrate the significance of precisely how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, supported by the use of statistical emulators for a full exploration of the parameter space.

\subsection*{Methods}

We employ game theory to define a signalling game representative of a scenario where pregnant women decide how far to disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether a costly referral should be made. This game is then recast as two games taking play against nature, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser, and a \ac{CPT} type.

Using a simulator we have developed in Python, we recreate two key qualitative trends described in the Midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
Finally a global sensitivity analysis using \acp{GEM} was conducted, to compare the response surfaces of the different decision rules in the game.

\subsection*{Results}

Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparitive heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making.

\subsection*{Conclusions}

The ability of all the decision rules to show the qualitative trends suggests that there is some utility associated with this approach.

\subsection*{Comments}

We note that the scenario omits the overwhelming complexity of the reality, and is presented largely in the spirit of a convenient demonstration of the methodology. Clearly a domain where there is sufficient data to permit a more comprehensive approach to validation of model outcomes is desirable, and will form the basis of our future work.

### 2014-07-05 Introduction.tex
Added tex  root for easier building
Making notes
Sketching out

\section{Introduction}
\label{sec:intro}
%CONTRIBUTION, FUCKER!
%Also, remember to say what you're going to do for the rest of the article?

>>>>

%!TEX root = disclosure_game.tex
\section{Introduction}
\label{sec:intro}
%CONTRIBUTION, FUCKER!
%Also, remember to say what you're going to do for the rest of the article?
%CONTRIBUTION
%	Agents are awesome
%	Decision theory is super awesome
%	'nice story to hang it on'

The case in favour of \ac{ABM} as an approach has been made numerously, and elegantly REFS. As such we will not belabour the point, and instead turn to addressing some of the concerns often expressed about the method. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded.

%Finishing up

The remainder of this paper proceeds to provide small reviews of alcohol and disclosure in the maternity setting (\ref{sub:alcohol_disclosure}), and the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

### 2014-07-05 Model.tex
Added tex  root for easier building
Making notes
Sketching out

\section{Model}
\label{sec:model}
%Start this off with a brief description of our fictional scenario.

\subsection{Disclosure Game}
\label{sub:the_game}
%Outline how the scenario translates into a game.

\subsection{Agent Models}
\label{sub:the_agents}
%Outline basic structure, then specifics on each one.
%This should probably go lexic -> bayes payoff -> bayes -> CPT in order
% of complexity.

>>>>

%!TEX root = disclosure_game.tex
\section{Model}
\label{sec:model}
%Start this off with a brief description of our fictional scenario.
% Whole section ~ 1.5K

\subsection{Disclosure Game}
\label{sub:the_game}
%Outline how the scenario translates into a game.
%Brief mention of the game theoretic solution

In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals. We also make the simplifying assumption that a woman may have one of only three drinking patterns - light, moderate, or heavy. Correspondingly, they are limited in what signals they may send to claiming to be one of these three types.

Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed not to impact on their choice of response, which is either to refer the woman for specialist treatment, or to do nothing.

At the end of a game, each player receives a payoff dependent on the actions and types of both players, which has a partially common interest component. Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it. Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care.

Agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{THINGY}.

%Might belong in a more methody bit? Read some stuff to check..
Women are drawn in order from a queue, and play against a midwife chosen at random. They play for a maximum of 12 rounds (following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred. At which point a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly.

Midwives play for \(k\) rounds (\(k=1000\) in all experiments), and conduct appointments in parallel. Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

\subsection{Agent Models}
\label{sub:the_agents}
%Outline basic structure, then specifics on each one.
%This should probably go lexic -> bayes payoff -> bayes -> CPT in order
% of complexity.
%suggest there are added shells of complexity
%		mention the info sharing because homophilly
%			related - the enhancement to the bayes/cpt agents is that they personalise, as much as anything.
%		properly explain dirichlet priors
% How about comparing the decision problem representation for the agent types?

While in principle a wide variety of agent models, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), motivated as in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; a Bayesian risk minimisation rule using the same information (2); a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \cite{Hau2008} agent (4) which is identical with 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.

As noted in section \ref{sub:the_game}, agents have perfect recall, and recognise individual opponents if they encounter them subsequently. While agents recall perfectly and make use of the new information for retrospective updates, their decisions are made \'as-if\' they were facing a new opponent.

\subsubsection{Payoff Reasoning}

Both payoff reasoners assume a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between lotteries. The lexicographic heuristic (algorithm \ref{alg:lexicographic}) maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. The Bayesian risk minimisation agent uses the same subset of information, but updates beliefs on the link between actions and payoffs using Bayes rule, and attempts to choose the action which minimises risk.

\subsubsection{Bayesian Risk Minimisation}

Aside from the heuristic agent, the remaining three agent types use Bayesian updating to attempt to improve
the accuracy of their beliefs. Given the discrete nature of agent
types, and actions, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed. The probability
density function takes the form -

\[
D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
\]

Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\)is the number
of discrete types, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the
psuedo-count of prior observations for type \(i\).

The distribution is particularly convenient, in that to infer the
probability of a new observation being of some particular type becomes
simply -

\begin{equation}
P(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
\end{equation}

Where \(n_{j}\) is simply the count of occurrences of type \(j\), so
that the belief that a new observation is of type \(j\) the number
of times that type has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast, and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.

\subsubsection{Descriptive Decision Theory}

\subsection{Information Sharing}
\label{sub:info_sharing}

It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups. This takes the form of having each agent share their memories with their colleagues with some probability \(p\). Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\). Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but the assumption is that only current news is relevant.}

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this outside information differently. The simple payoff based rule relys on a belief structure relating actions directly to rewards. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that generalises the new information.

\subsection{Model Implementation}
\label{sub:the_code}
% Use this bit to talk about the practical version of the game and where info is revealed?
The model itself is implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game}, together with full parameter sets, raw data, and all other code used in producing this paper.
